Whats reported in the news?

### 2018-03-12 paper/docs/04_Modelresults_50.Rmd
add 50k model

library(igraph)
library(corrplot)
library(patchwork)
library(ggpmisc)
library(ggraph)
library(ggiraph)
library(tidygraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales
library(viridis)     # Viridis color scales

@@

rm(list=ls())
col <- brewer.pal(6,"Dark2")
source("func/functions.R")
```

```{r caching, echo = FALSE}
load("../output/btw_out.Rda")
```

I conduct a STM (Strucutral Topic Model) estimation on a sample of 11,919 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de. The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.). I first extract all online articles using the the [Eventregistry API](http://eventregistry.org/documentation). Then all articles from the section "domestic policy" are filtered by checking the URL structure.

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[1], alpha= .8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[2]) +
  scale_color_manual(values = col) +
  labs(x="", y="number of articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

```{r echo = FALSE}
load("../output/models/STM 35 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

```{r eval=FALSE, fig.height=12, fig.width=5, include=FALSE}
topic <- 35

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election Results", 8, "Seehover vs. Söder, CSU", 9, "EU policies, refugee policy", 10, "German Parliament, parliamentarians", 11, "Mix: DIE LINKE, W.Schäuble", 12, "Refugees, deportation", 13, "Mix: Schröder, IT Topics", 14, "B90/Die Grünen", 15, "USA, Russia, Israel", 16, "Great coalition", 17, "A.Weidel (AfD)", 18, "Budget statistics, Welfare policy", 19, "Process Error", 20, "Federal Constitutional Court, Ministry of the Interior", 21, "German armed forces, Mali", 22, "Mix: Weather, DB, nuclear transport, ...", 23, "Elections in Niedersachsen", 24, "CDU / CSU", 25, "Mix: political talkshows, Berxit, Macron", 26, "Mix: F.-W.Steinmeier, Constitution, H.Maas", 27, "public statistics", 28, "Election polls", 29, "F.Petry, Gauland (AfD)", 30, "Mix: NSU, sexism", 31, "German armed forces, V.d.Leyen", 32, "G20 in Hamburg", 33, "Turkey, S.Gabriel", 34, "police reports, terror (left-, right-wing, IS)", 35, "Seehofer, refugee cap"), ncol=2, byrow=T)

@@

Next, we can assign a topic to each document (topic with highest postertior gamma)

```{r Extract wtp and dtp}
# Document-topic probabilities
stmOut %>% tidy("theta") -> theta

top_topics <- theta %>% 
  group_by(document) %>%
  mutate(therank = rank(-gamma)) %>%
  filter(therank == 1) %>%
  select(- therank)

@@

##### How is the top-gamma value distributed among the corpus?

```{r}
btw.2 %>%
  ggplot(aes(gamma)) +
  geom_density(color = col[3],
               fill = col[3], alpha=.7) +
  labs(x="Distribution of gamma value")
```

#### Inspect the unclear topics
```{r eval=FALSE, include=FALSE}
btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
  arrange(desc(gamma)) %>%
  top_n(10) %>%
  htmlTable::htmlTable(align="l")
```

@@

```{r fig.height=6}
p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

@@

```{r fig.height=8, fig.width=12}
p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
  geom_col(fill = col[3]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

```{r}
keep <- c(1,16,24,29,3,6,8)
```

@@

```{r}
effect <- estimateEffect(c(1:k) ~site+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
```

@@

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("site", "", parameter),
         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

@@

```{r fig.height=8, fig.width=12}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

The following figure shows the regression results for each month. The coefficients indicate the deviation from the base value of June 2017 (keeping the news source).

```{r fig.height=8, fig.width=12}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(!parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  filter(parameter != "(Intercept)") %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

```{r}
sent <- c(
  # positive Wörter
  readLines("dict/SentiWS_v1.8c_Negative.txt",
            encoding = "UTF-8"),
  # negative Wörter
  readLines("dict/SentiWS_v1.8c_Positive.txt",
            encoding = "UTF-8")
) %>% lapply(function(x) {
  # Extrahieren der einzelnen Spalten
  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
  return(data.frame(words = res[1], value = res[2],
                    stringsAsFactors = FALSE))
}) %>%
  bind_rows %>% 
  mutate(word = gsub("\\|.*", "", words) %>% tolower,
         value = as.numeric(value)) %>% 
  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.8) %>%
  filter(topic %in% keep)

@@

# Combine with sentiment values
sentDF <- left_join(token, sent, by="word") %>% 
  mutate(value = as.numeric(value)) %>% 
  #filter(!is.na(value)) %>%
  mutate(polarity = ifelse(value < 0, "negative", "NA"),
         polarity = ifelse(value > 0, "positive", polarity))
```

@@

calculate sentiment value of document $d$:

$$
\text{Sentiment}_d = \frac{|\text{Sum of positive tokens}_d| - |\text{Sum of negative tokens}_d|}{\text{Number ot tokens}_d}
$$

```{r}
sentDF.values <- sentDF %>%
  select(document, word, value, polarity) %>%
  mutate(id = row_number()) %>%
  spread(polarity, value) %>%
  group_by(document) %>%

  # calculate sum of positive and negative values
  summarise(sum_positive = sum(positive, na.rm = T),
            sum_negative = sum(negative, na.rm = T)) %>%

  # calculate diff
  mutate(sent_diff = abs(sum_positive) - abs(sum_negative)) %>%

  # combine with dataframe
  left_join(., df, 
            by = "document") %>%
  # calculate sentiment
  mutate(sentiment = sent_diff / text_length)
```

### Plot Sentiment

#### 1. by topic
```{r fig.height=8, fig.width=6}
p <- sentDF.values %>%
  group_by(topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[1], alpha = 0.7) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

#### 2.by site

```{r}
p <- sentDF.values %>%
  group_by(site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, aes(reorder(site, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[3], alpha = 0.7) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

#### 3. By site and topic

```{r fig.height=8, fig.width=12}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment, label = obs)) +
  geom_col(fill=col[1], alpha = 0.7) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="", fill= "Number of\nObservations",
       title = "Sentiment value") +
  theme(axis.text.y = element_text(size=12))
```

```{r}
sentDF.values %>%
  filter(topic == 6) %>%
  select(title, sentiment, site) %>%
  htmlTable::htmlTable(align = "l")
```

### Radar plot

@@

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "")
```

```{r}
for (i in stmOut$settings$covariates$yvarlevels) {

@@

}

@@

### Compare with polls
```{r eval=FALSE, include=FALSE}
load("../output/polls.Rda")
```

Define Functions

@@

Prepare Dataframes

@@

Plot

>>>>

library(igraph)
library(corrplot)
library(patchwork)
library(ggpmisc)
library(ggraph)
library(ggiraph)
library(tidygraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales

@@

rm(list=ls())
col <- rcartocolor::carto_pal(12, "Bold")
source("func/functions.R")
```

```{r caching, echo = FALSE}
load("../output/btw_out2.Rda")
```

I conduct a STM (Strucutral Topic Model) estimation on a sample of 14,936 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de. The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.). I first extract all online articles using the the [Eventregistry API](http://eventregistry.org/documentation). Then all articles from the section "domestic policy" are filtered by checking the URL structure.

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[8], alpha = 0.8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[5]) +
  scale_color_manual(values = col) +
  labs(x="", y="number of articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

```{r echo = FALSE}
load("../output/models/STM 50 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

```{r eval=FALSE, fig.height=12, fig.width=5}
topic <- 50

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "B90/ Die Grüne", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs. Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Decision about GroKo in the SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs. Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public budget statistics, Education and Healthcare", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)

@@

## Posterior distribution (gamma)

The theta Matrix is a DxK Matrix that gives us a probability for each topic (K) and each document (D)

```{r Extract wtp and dtp}
# Document-topic probabilities
stmOut %>% tidy("theta") -> theta
```

The probability of each topic for documents 1-5 can be plotted as:

```{r}
theta %>%
  filter(document < 6) %>%
  ggplot(aes(factor(topic), gamma, 
             fill = factor(document))) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = col,
                    guide = guide_legend(
                      nrow = 1
                    )) +
  labs(x = "Topic", fill = "Document",
       title = "Gamma distribution of documents 1-5") +
  theme(legend.position = "bottom") 
```

As you can see, only document 2 cannot be assigned to any topic with a high probability. In the case of the other documents, it is highly likely that it belongs to a particular topic.

To get a better understanding of the distribution of the "highest gamma", we assign a topic to each document (topic with highest postertior distribution).

```{r}
top_topics <- theta %>% 
  group_by(document) %>%
  mutate(therank = rank(-gamma)) %>%
  filter(therank == 1) %>%
  select(- therank)

@@

```{r}
ggplot(btw.2, aes(gamma)) +
  geom_density(fill=col[3], alpha = 0.8,
               color = col[3]) +
  labs(title = "Density Plot / Posterior distribution",
       y = "Theta")
```

```{r eval=FALSE, include=FALSE}
# Inspect the unclear topics
btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
  arrange(desc(gamma)) %>%
  top_n(10) %>%
  htmlTable::htmlTable(align="l")
```

@@

```{r fig.height=8, fig.width=6}
p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

@@

```{r fig.height=8, fig.width=12}
p2 <- freq %>%
  mutate(topic =  as.numeric(gsub(":.*$","",topic))) %>% 
  ggplot(aes(reorder(topic_name,topic), freq)) +
  geom_col(fill = col[3]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

```{r}
keep <- c(1,2,4,10,13,17,20,22,26,27,37,46)
```

@@

```{r}
effect <- estimateEffect(c(1:k) ~site, stmOut, 
                         metadata = out$meta, uncertainty = "None")
```

@@

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("site", "", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

@@

```{r fig.height=4, fig.width=10}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

@@

```{r}
sent <- c(
  # positive Wörter
  readLines("dict/SentiWS_v1.8c_Negative.txt",
            encoding = "UTF-8"),
  # negative Wörter
  readLines("dict/SentiWS_v1.8c_Positive.txt",
            encoding = "UTF-8")
) %>% lapply(function(x) {
  # Extrahieren der einzelnen Spalten
  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
  return(data.frame(words = res[1], value = res[2],
                    stringsAsFactors = FALSE))
}) %>%
  bind_rows %>% 
  mutate(word = gsub("\\|.*", "", words) %>% tolower,
         value = as.numeric(value)) %>%
  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
  group_by(word) %>% summarise(value = mean(value)) %>% ungroup

# sent %>% 
#   dplyr::top_n(10, desc(value)) %>%
#   htmlTable::htmlTable()
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.85) %>%
  filter(topic %in% keep)

@@

# Combine with sentiment values
sentDF <- left_join(token, sent, by="word") %>% 
  mutate(value = as.numeric(value)) %>% 
  #filter(!is.na(value)) %>%
  mutate(negative = ifelse(value < 0, value, NA),
         positive = ifelse(value > 0, value, NA),
         negative_d = ifelse(value < 0, 1, 0),
         positive_d = ifelse(value > 0, 1, 0)) 
```

##### Check the analysis for a set of example documents.

```{r}
sentDF %>% filter(document == unique(sentDF$document)[1]) %>%
  select(title, word, value, site) %>%
  htmlTable::htmlTable(align = "l")
```

@@

We apply two different measurements:

  1. **Weighted** calculates the score based on the weighted values for a word. As explained above, the dictionary places the words on an interval of -1 and 1. The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document.

$$
\text{Weighted}_d = \frac{|\text{positive polarity score}_d| - |\text{negative polarity score}_d|}{\text{Total Words}_d}
$$

  2. **Count** calculates the score as the difference of positive and negative words (dummy) divided divided by the total number of words in that document. This value therefore only reflects the relation between positive and negative words, without considering the weighting of these words.

$$
\text{Count}_d = \frac{\text{Sum of positive Words}_d - \text{Sum of negative Words}_d}{\text{Total Words}_d}
$$

```{r}
sentDF.values <- sentDF %>%
  select(document, word, value, 
         negative, positive,
         negative_d, positive_d) %>%
  group_by(document) %>%

  # calculate sum of positive and negative values
  summarise(sum_positive = sum(positive, na.rm = T),
            sum_negative = sum(negative, na.rm = T),
            sum_positive_d = sum(positive_d, na.rm = T),
            sum_negative_d = sum(negative_d, na.rm = T)) %>%

  # calculate diff
  mutate(sent_diff = sum_positive + sum_negative,
         sent_diff_d = sum_positive_d - sum_negative_d) %>%

  # combine with dataframe
  left_join(., df, 
            by = "document") %>%
  # calculate sentiment
  mutate(sentiment_d = sent_diff_d / text_length,
         sentiment = sent_diff / text_length)
```

#### 4. Plot Sentiment

##### 4.1. by topic
```{r fig.height=4, fig.width=7}
p <- sentDF.values %>%
  group_by(topic_name) %>%
  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
            sentiment = mean(sentiment, na.rm=T),
            obs = n())

## weighted ##
p1 <- ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[1], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Weighted") +
  theme(axis.text.y = element_text(size = 8))

## unweighted ##
p2 <- ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment_d,
              label = obs)) +
  geom_col(fill = col[4], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Count") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

p1 + p2
```

##### 4.2. by site

```{r fig.height=4, fig.width=7}
p <- sentDF.values %>%
  group_by(site) %>%
  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
            sentiment = mean(sentiment, na.rm=T),
            obs = n())

## weighted ##
p1 <- ggplot(p, aes(reorder(site, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[1], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Weighted") +
  theme(axis.text.y = element_text(size = 8))

## unweighted ##
p2 <- ggplot(p, aes(reorder(site, sentiment), 
              sentiment_d,
              label = obs)) +
  geom_col(fill = col[4], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Count") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

p1 + p2
```

##### 4.3. By site and topic

```{r fig.height=8, fig.width=12}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            sentiment_d = mean(sentiment_d, na.rm=T),
            obs = n())

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment, label = obs)) +
  geom_col(fill=col[1], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "Weighted") +
  theme(axis.text.y = element_text(size=8))

p2 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_d, label = obs)) +
  geom_col(fill=col[4], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "Count") +
  theme(axis.text.y = element_text(size=8))

p1 + p2 + plot_layout(ncol = 1)
```

##### 4.4. Radar plot

@@

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Weighted")
```

```{r eval=FALSE, include=FALSE}
for (i in stmOut$settings$covariates$yvarlevels) {

  ggsave(p, filename = paste0("../figs/radarchartWeighted_",i,k,".png"), 
         device = "png", dpi = 600)

```{r}
sentDF.values %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment_d, na.rm=T)) %>%
  spread(key=topic_name, value=sentiment) -> radar

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Count")
```

```{r eval=FALSE, include=FALSE}
for (i in stmOut$settings$covariates$yvarlevels) {

@@

###### Weighted

<img src="../figs/radarchartWeighted_Bild.de35.png", width = "49%">
<img src="../figs/radarchartWeighted_DIE WELT35.png", width = "49%">
<img src="../figs/radarchartWeighted_FOCUS ONLINE35.png", width = "49%">
<img src="../figs/radarchartWeighted_SPIEGEL ONLINE35.png", width = "49%">
<img src="../figs/radarchartWeighted_stern.de35.png", width = "49%">
<img src="../figs/radarchartWeighted_Tagesschau.de35.png", width = "49%">
<img src="../figs/radarchartWeighted_ZEIT ONLINE35.png", width = "49%">

###### Count

@@

### 5. SenitmantR

```{r}
pacman::p_load(sentimentr)
```

```{r}
sent %>%
  mutate(polarity = value) %>%
  as_key() -> sentiment_df
```

#### Output

We may wish to see the output from sentiment_by line by line with positive/negative sentences highlighted. The highlight function wraps a sentiment_by output to produces a highlighted HTML file (positive = green; negative = pink). Here we look at a random article for each site.

```{r}
df %>% 
  mutate(text_split = get_sentences(text)) %$%
  sentiment(text_split,
               polarity_dt = sentiment_df) -> df_sent

df %>% 
  group_by(site) %>%
  sample_n(1) %>%
  mutate(text_split = get_sentences(title_text)) %$%
  sentiment_by(text_split, site,
               polarity_dt = sentiment_df) %>%
  sentimentr::highlight()
```

[Polarity](polarity.html)

<!-- ### 5. Compare with polls -->

```{r eval=FALSE, include=FALSE}
load("../output/polls.Rda")

htmlTable::htmlTable(table[1:10,], align = "l")
```

<!-- Define Functions  -->

@@

<!-- Prepare Dataframes -->

@@

<!-- Plot  -->
